DNSKEY Management

### 2012-12-03 paper/paper.tex
Add paragraph about cost of DNSSEC @ SWITCH
Add abstract

@@

>>>>

\begin{abstract}
  In this paper we recapitutale the current deployment status of
  DNSSEC and go into the main issues when managing its keys. It
  outlines the paper ``Interadministrative Challenges in Managing
  DNSKEYs'' and updates some of its contents especially with respect
  to the signing of the root zone on July 15, 2012. We will see that
  DNSSEC penetration in the Internet's zones is still low but that the
  necessary foundations have been lain for full deployment.
\end{abstract}

@@

\paragraph{Cost} DNSSEC secure delegation is currently provided by
SWITCH with no additional cost to normal DNS delegation.
